---
title: "1_Munging_Data"
author: "Brandon D. Hoenig"
date: '2022-06-15'
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r}
library(tidyverse)
```


File for Fulcrum Export before app crashed. 
```{r}
#Fulcrum_Export_e9d9f1d9-dd61-4d04-a39c-e28cee0e156f
```

```{r}
Amphibian_Processing_App_old <-
  read_csv('Data/FulcrumDataExports/Fulcrum_Export_e9d9f1d9-dd61-4d04-a39c-e28cee0e156f/ple_amphibian_survey/ple_amphibian_survey.csv') %>% 
  group_by(fulcrum_id) %>% 
  top_n(1, version) %>% 
  ungroup() %>% 
  select(fulcrum_id, created_at, location, date,survey_comments) %>%
  mutate(processor = "Brandon Hoenig", 
         processor_other = NA) %>% unique()

Amphibian_Processing_App_Repeatable_old <-
  read_csv("Data/FulcrumDataExports/Fulcrum_Export_e9d9f1d9-dd61-4d04-a39c-e28cee0e156f/ple_amphibian_survey/ple_amphibian_survey_amphibian_capture_survey_collections.csv") %>% 
  group_by(fulcrum_id) %>%
  top_n(1, version) %>% 
  ungroup() %>% 
      mutate(amp_id_1 = NA, 
             amp_id_2 = NA, 
             amp_id_3 = NA, 
             amp_id_4 = NA, 
             antibody_id_1 = NA,
             antibody_id_2 = NA, 
             antibody_id_3 = NA,
             antibody_id_4 = NA,
             crispr_swab_tube_id = NA,
             dry_swab_tube_id = NA) %>%
  select(fulcrum_id, created_at, fulcrum_parent_id, created_at, bag_id, species_capture, species_capture_other, capture_type, capture_type_other, capture_mark_recapture, life_stage, life_stage_other, sex, sex_other, snout_vent_length, body_and_bag_mass, bag_mass, body_mass, bd_swab_tube_id, crispr_swab_tube_id, bacterial_swab_tube_id, mucusome_id, amp_id_1, amp_id_2, amp_id_3, amp_id_4, antibody_id_1, antibody_id_2, antibody_id_3, antibody_id_4, toe_clip_tube_id, capture_comments, time_of_capture, body_temperature, microhabitat_type, microhabitat_temperature) %>% unique()

Amphibian_Survey_old <-
  read_csv("Data/FulcrumDataExports/Fulcrum_Export_e9d9f1d9-dd61-4d04-a39c-e28cee0e156f/ple_amphibian_survey/ple_amphibian_survey.csv") %>% 
  group_by(fulcrum_id) %>% 
  top_n(1, version) %>% 
  ungroup() %>% 
  select(location, fulcrum_id, created_at, date, observers, other_observers,humidity, pressure, elevation, wind_speed_ms, air_temperature_c, dissolved_oxygen, water_temperature_c, conductivity_us, ph, sampling_event_comments) %>%
  mutate(edna_volume_collected_l = NA,
         edna_water_collected = NA) %>% unique()

Amphibian_Captured_Information_old <-
  read_csv('Data/FulcrumDataExports/Fulcrum_Export_e9d9f1d9-dd61-4d04-a39c-e28cee0e156f/captured_amphibian_information/captured_amphibian_information.csv') %>% 
  group_by(fulcrum_id) %>% 
  top_n(1, version) %>% 
  ungroup() %>% 
  select(fulcrum_id, created_at, observer, observer_other, date, location, start_time, end_time)  %>% unique()

Amphibian_Captured_Information_Repeatable_old <-
  read_csv('Data/FulcrumDataExports/Fulcrum_Export_e9d9f1d9-dd61-4d04-a39c-e28cee0e156f/captured_amphibian_information/captured_amphibian_information_captured_amphibian_information.csv') %>%
  group_by(fulcrum_id) %>% 
  top_n(1, version) %>% 
  select(fulcrum_id, created_at, fulcrum_parent_id, bag_id, time_of_capture, body_temperature, microhabitat_type, microhabitat_temperature, bag_photo) %>%
  mutate(species = NA) %>% unique()

CMR_Data_old <-
  read_csv('Data/FulcrumDataExports/Fulcrum_Export_e9d9f1d9-dd61-4d04-a39c-e28cee0e156f/ple_cmr_data/ple_cmr_data.csv') %>% 
  select(fulcrum_id, created_at, location, species, capture_date, cmr_id, cmr_id_other) 
```


Current Fulcrum Data Exports Folder
```{r}
#Fulcrum_Export_2ad93ec7-9001-4e9a-8918-1746456193fb
```


Read in data from Fulcrum exports, filter out repeated records and 
```{r}
Acoustic_Survey <-
  read_csv('Data/FulcrumDataExports/Fulcrum_Export_2ad93ec7-9001-4e9a-8918-1746456193fb/ple_acoustic_survey/ple_acoustic_survey.csv') %>% 
  group_by(fulcrum_id) %>% 
  top_n(1, version) %>% 
  filter(change_type != 'delete') %>% 
  select(fulcrum_id, created_at, observer, observer_other, date, location, start_time, end_time) %>% unique()

Acoustic_Survey_Repeatable <-
  read_csv('Data/FulcrumDataExports/Fulcrum_Export_2ad93ec7-9001-4e9a-8918-1746456193fb/ple_acoustic_survey/ple_acoustic_survey_acoustic_survey.csv') %>%
  group_by(fulcrum_id) %>% 
  top_n(1, version) %>% 
  ungroup() %>%
  select(fulcrum_id, created_at, fulcrum_parent_id, species_acoustic, call_index, acoustic_comments) %>% unique()

Amphibian_Processing_App <-
  read_csv('Data/FulcrumDataExports/Fulcrum_Export_2ad93ec7-9001-4e9a-8918-1746456193fb/ple_amphibian_processing_app/ple_amphibian_processing_app.csv') %>% 
  group_by(fulcrum_id) %>% 
  top_n(1, version) %>% 
  filter(change_type != 'delete') %>%
  ungroup() %>% 
  select(fulcrum_id, created_at, location, date, processor, processor_other, survey_comments) %>%
  bind_rows(., Amphibian_Processing_App_old) %>% unique()

Amphibian_Processing_App_Repeatable <-
  read_csv("Data/FulcrumDataExports/Fulcrum_Export_2ad93ec7-9001-4e9a-8918-1746456193fb/ple_amphibian_processing_app/ple_amphibian_processing_app_amphibian_capture_survey_collections.csv") %>%
  group_by(fulcrum_id) %>% 
  top_n(1, version) %>%
  select(fulcrum_id, created_at, fulcrum_parent_id, created_at, bag_id, species_capture, species_capture_other, capture_type, capture_type_other, capture_mark_recapture, life_stage, life_stage_other, sex, sex_other, snout_vent_length, body_and_bag_mass, bag_mass, body_mass, bd_swab_tube_id, dry_swab_tube_id, crispr_swab_tube_id, bacterial_swab_tube_id, mucusome_id, amp_id_1, amp_id_2, amp_id_3, amp_id_4, antibody_id_1, antibody_id_2, antibody_id_3, antibody_id_4, toe_clip_tube_id) %>%
  bind_rows(Amphibian_Processing_App_Repeatable_old) %>% unique()

Amphibian_Survey <-
  read_csv("Data/FulcrumDataExports/Fulcrum_Export_2ad93ec7-9001-4e9a-8918-1746456193fb/ple_amphibian_survey/ple_amphibian_survey.csv") %>% 
  group_by(fulcrum_id) %>% 
  top_n(1, version) %>% 
  filter(change_type != 'delete') %>%
  ungroup() %>%
  select(location, created_at, date, observers, other_observers, edna_water_collected, edna_volume_collected_l, humidity, pressure, elevation, wind_speed_ms, air_temperature_c, dissolved_oxygen, water_temperature_c, conductivity_us, ph, sampling_event_comments) %>%
  bind_rows(Amphibian_Survey_old) %>% unique()

Amphibian_Captured_Information <-
  read_csv('Data/FulcrumDataExports/Fulcrum_Export_2ad93ec7-9001-4e9a-8918-1746456193fb/ple_captured_amphibian_information/ple_captured_amphibian_information.csv') %>% 
  group_by(fulcrum_id) %>% 
  top_n(1, version) %>% 
  filter(change_type != 'delete') %>%
  ungroup() %>% 
  select(fulcrum_id, created_at, observer, observer_other, date, location, start_time, end_time, survey_comments) %>%
  bind_rows(Amphibian_Captured_Information_old) %>% unique()

Amphibian_Captured_Information_Repeatable <-
  read_csv('Data/FulcrumDataExports/Fulcrum_Export_2ad93ec7-9001-4e9a-8918-1746456193fb/ple_captured_amphibian_information/ple_captured_amphibian_information_captured_amphibian_information.csv') %>%
  group_by(fulcrum_id) %>% 
  top_n(1, version) %>% 
  select(fulcrum_id, created_at, species, fulcrum_parent_id, bag_id, time_of_capture, body_temperature, microhabitat_type, microhabitat_temperature, bag_photo) %>%
  rbind(Amphibian_Captured_Information_Repeatable_old) %>% unique()

VisualEncounter_Survey <-
  read_csv("Data/FulcrumDataExports/Fulcrum_Export_2ad93ec7-9001-4e9a-8918-1746456193fb/ple_visual_encounter_survey/ple_visual_encounter_survey.csv")  %>%
  group_by(fulcrum_id) %>% 
  top_n(1, version) %>% 
  select(fulcrum_id, created_at, observer, observer_other, date, location, start_time, end_time) %>% 
  unique() 

VisualEncounter_Survey_Repeatable <-
  read_csv('Data/FulcrumDataExports/Fulcrum_Export_2ad93ec7-9001-4e9a-8918-1746456193fb/ple_visual_encounter_survey/ple_visual_encounter_survey_visual_encounter_information.csv')  %>%
  group_by(fulcrum_id) %>% 
  top_n(1, version) %>% 
  select(fulcrum_id, created_at, fulcrum_parent_id, species_ves, species_ves_other, count_ves, comments_ves) %>%
  unique()

CMR_Data <-
  read_csv('Data/FulcrumDataExports/Fulcrum_Export_2ad93ec7-9001-4e9a-8918-1746456193fb/ple_cmr_data/ple_cmr_data.csv') %>% 
  select(fulcrum_id, created_at, location, species, capture_date, cmr_id, cmr_id_other) %>%
  bind_rows(CMR_Data_old) %>% unique()
```

Remove all files with the '_old' suffix so that we don't write those data in the next step.  We don't need duplicates as those data are in the files not marked with the '_old' suffix. 
```{r}
rm(list = ls()[grep("_old", ls())])
```


For loop to write all munged data files into new csvs.  This removes all of the extra Fulcrum-related data that is unrelated to the collection data. These files are found in the 'Output' folder. 
```{r}
files <- mget(ls())

for (i in 1:length(files)){
  write.csv(files[[i]], paste("Output/Munged_data/munged_", names(files[i]), ".csv", sep = ""))
}
```



